The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
nobs edits
reflow
why opt

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
fixed rate (eg every $x$ minutes or hours) continuously throughout the study
period. We investigated the influence of the number of observations on resulting
multilayer networks. We randomly selected 500 timesteps and iteratively included
25 additional observations, regenerating the multilayer network and calculating
associations of individuals. Subsequent iterations included the previous set of
observations to mimic collection of observational data. <!-- TODO: bah conclude
/ this sentence falls off a cliff -->

# Scale in multilayer networks in practice: case study results and discussion
<!-- TODO: Add intro/general to results? with mention figures are means of inds-->
<!-- TODO: make sure we clarify these are means of all individuals? -->
<!-- TODO: discuss layer similarity for social threshold -->

In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased to
~100-200 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks (Figure
\@ref(fig:socres)b). Connective redundancy increased rapidly when groups were
formed up to ~100 m threshold, followed by a plateau and slight decrease at
higher thresholds, presumably due to an increase in summer forest degree at ~500
m (Figure \@ref(fig:socres)d). Taken together, these results suggest the optimal
social scale at which groups should be assigned is likely somewhere between
~20 - 100 m based on the rate at which network metrics stabilized. For ungulates,
groups are often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al.
2018; Peignier et al. 2019), suggesting that given similar quantities of data,
~50 m is likely an appropriate social scale for generating social networks in caribou
and similar species.
<!-- TODO: missing summer relevance and all layer similarily-->

>>>>

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
fixed rate, eg. every $x$ minutes or hours, continuously throughout the study
period. We investigated the influence of the number of observations on resulting
multilayer networks. We randomly selected 500 timesteps and iteratively included
25 additional observations, regenerating the multilayer network and calculating
associations of individuals. Subsequent iterations included the previous set of
observations to mimic collection of observational data. <!-- TODO: bah conclude
/ this sentence falls off a cliff -->

# Scale in multilayer networks in practice: case study results and discussion
<!-- TODO: Add intro/general to results? with mention figures are means of inds-->

<!-- TODO: make sure we clarify these are means of all individuals? -->
<!-- TODO: discuss layer similarity for social threshold -->

In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased to
~100-200 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks (Figure
\@ref(fig:socres)b). Connective redundancy increased rapidly when groups were
formed up to ~100 m threshold, followed by a plateau and slight decrease at
higher thresholds, presumably due to an increase in summer forest degree at ~500
m (Figure \@ref(fig:socres)d). Taken together, these results suggest the optimal
<!-- TODO: why optimal -->
social scale at which groups should be assigned is likely somewhere between ~20
- 100 m based on the rate at which network metrics stabilized. For ungulates,
groups are often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al.
2018; Peignier et al. 2019), suggesting that given similar quantities of data,
~50 m is likely an appropriate social scale for generating social networks in
caribou and similar species.
<!-- TODO: missing summer relevance and all layer similarily-->
